Classifying Patent Based on their Semantic Content \\ An empirical exploration into patent text mining

### 2018-11-27 Docs/Papers/Technical/overleafv2/Slides.tex

\begin{frame}{Estimation of n-gram relevance}

    \begin{itemize}
        \item Termhood-based selection of a fixed number of keywords $K_W = 100,000$ (\textit{difficulty to select terms in general})
        % bias to keep fixed size of vocabulary ?
        %  if variable = f(patents) -> arbitrary fixes a number of kws "per patent"; should them optimize regarding an exogenous criteria, which one ?
        %  if fixed, this number varies, so the resolution of classes varies, thus larger classes more recently ? peak in sizes contradicts that, so should not capture this bias significantly (or structure is more important).
        \item Estimation on temporal moving windows $\left[t - T_w ; t\right]$ (fixed to $T_W = 5y$ after sensitivity analysis)
        \item Filtering of network edge (parameter $\theta_w$), with an additional exogenous control by technological class keyword concentration to filter nodes (parameter $\theta_c$)
        % potential bias here -> would capture the exogenous classification system ? idem our results suggest that bias does not dominate results
        \item Low sensibility to the size of the time windows for the network structure % in comparable lengths of course
    \end{itemize}

@@

@@

\justify

@@

\begin{frame}{Evolution of patent diversities}
   \centering
    \includegraphics[width=\textwidth]{figures/Fig5.png}

@@

    $\rightarrow$ an impact of new information technologies ? (regarding knowledge production: from expert and contextualized to automatized search in references e.g.)

@@

\section{Conclusion}
\begin{frame}{Possible developments}
\textbf{Direct}
    \begin{itemize}
        \item Look at the correlation between patent quality indicators and centrality indices.
        \item Use patent-firm matching to study a \emph{firm-level} semantic network.
        \item Extending the analysis to other patent offices (EPO/JPO).
    \end{itemize}
    \pause
\textbf{Economic}
    \begin{itemize}
        \item Linking semantic measures to values of firms
        \item Can semantic proximity helps understand M\&A?
        \item Firms trajectories in relation to their life-cycle
    \end{itemize}
    \pause
\textbf{Technology}
\begin{itemize}
    \item Measure of complementarity between technology?
    \item Possible application to detection of emerging research fronts
    \item An interactive exploration of semantic content?
\end{itemize}
\end{frame}
\begin{frame}{Other projects}
    \justify

@@

\begin{frame}{Definition of termhood}

@@

\begin{frame}{Patent measures}

@@

    Directed simple modularity:
    \[
Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
\]

@@

>>>>

\begin{frame}{Estimation of n-gram relevance}\label{slide:relevance}

    \begin{itemize}
        \item Termhood-based selection of a fixed number of keywords $K_W = 100,000$ (\textit{difficulty to select terms in general}) \hyperlink{slide:filtration}{\beamerbutton{Definition}}
        % bias to keep fixed size of vocabulary ?
        %  if variable = f(patents) -> arbitrary fixes a number of kws "per patent"; should them optimize regarding an exogenous criteria, which one ?
        %  if fixed, this number varies, so the resolution of classes varies, thus larger classes more recently ? peak in sizes contradicts that, so should not capture this bias significantly (or structure is more important).
        \item Estimation on temporal moving windows $\left[t - T_w ; t\right]$ (fixed to $T_W = 4y$ after sensitivity analysis)
        \item Filtering of network edge (parameter $\theta_w$), with an additional exogenous control by technological class keyword concentration to filter nodes (parameter $\theta_c$)
        % potential bias here -> would capture the exogenous classification system ? idem our results suggest that bias does not dominate results
        \item Low sensibility to the length of the time window for the network structure  
\hyperlink{slide:sensitivity}{\beamerbutton{Sensitivity analysis}}
% in comparable lengths of course
    \end{itemize}

\begin{frame}{Technical aspects}

	$\rightarrow$ Temporal complexity: $\mathcal{O}(N_P)$ for keyword extraction and co-occurrences (constant $l_{max}^2$); parallelization on a 60 cores server for a ``reasonable'' computation time.

	$\rightarrow$ Memory complexity: co-occurrence matrices in $\mathcal{O}(K_W^2)$; necessitates around 600Go RAM when parallelized.

	$\rightarrow$ Database management: MongoDB (nosql suited to big data).

\begin{frame}{An application of the method to a scientific corpus}
	 % illustration de la flexibilite de la methode

	 \includegraphics[width=0.49\textwidth]{figures/cyb_Fig6.jpg}
	 \includegraphics[width=0.49\textwidth]{figures/cyb_Fig8.jpg}

	\textit{The method has been applied to a scientific corpus; adaptation of optimization procedures as the topological structure is different.} \cite{raimbault2017exploration}

@@

    \hyperlink{slide:sensitivity}{\beamerbutton{Sensitivity analysis}}

@@

%\justify

@@

\begin{frame}{Evolution of patent diversities}

\label{slide:diversity}
\hyperlink{slide:measures}{\beamerbutton{Back}}

   \centering
    \includegraphics[width=\textwidth]{figures/Fig5.png}

@@

    $\rightarrow$ an impact of new information technologies (regarding knowledge production: from expert and contextualized to automatized search in references e.g.) ? Linked to structural changes in economy (increase in firm concentration since 90s) ?

@@

\section{Conclusion}
\begin{frame}{Possible developments}
\textbf{Direct}
    \begin{itemize}
        \item Look at the correlation between patent quality indicators and centrality indices.
        \item Use patent-firm matching to study a \emph{firm-level} semantic network.
        \item Extending the analysis to other patent offices (EPO/JPO).
    \end{itemize}
    \pause
\textbf{Economic}
    \begin{itemize}
        \item Linking semantic measures to values of firms
        \item Can semantic proximity helps understand M\&A?
        \item Firms trajectories in relation to their life-cycle
    \end{itemize}
    \pause
\textbf{Technology}
\begin{itemize}
    \item Measure of complementarity between technology?
    \item Possible application to detection of emerging research fronts
    \item An interactive exploration of semantic content?
\end{itemize}
\end{frame}

\begin{frame}{Other projects}
    %\justify

@@

\begin{frame}{Filtration measures}

\label{slide:filtration}
\hyperlink{slide:relevance}{\beamerbutton{Back}}

    \textit{1. Unithood: n-gram specific frequency-based filtration ($4\cdot K_W$ keywords)}

	\[
	u_i = f_i\cdot \log{(1 + l_i)}
	\]

    \textit{2. Termhood: chi-square statistic for the uniformity of co-occurences}

    \begin{eqnarray}
\label{termhood}
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
\end{eqnarray}

	\textit{3. Edge weight filtration with a threshold of $\theta_w = \theta_w^{(0)}\cdot N_P$}

	\textit{4. Node filtration with a threshold $\theta_c$ on technological class concentration given by}

    \[
    c_{tech}(s) = \displaystyle \sum_{j=1}^{N^{(tec)}} \frac{k_j(s)^2}{ \left(\sum_i k_i(s)\right)^2}
    \]

@@

\begin{frame}{Patent measures}
\label{slide:measures}
\hyperlink{slide:diversity}{\beamerbutton{Back}}

    \textit{Diversity}
    \[
D_i^{(z)} = 1 - \sum_{j =1}^{N^{(z)}} {p_{ij}^2}, \text{ with } z \in \{tec, sem\}
	\]

	\textit{Originality and Generality}

	\[
O_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in I_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in I_i}{p_{i'k}}}}\right)^2}
\text{ and } G_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'k}}}}\right)^2}
\]

@@

    Directed simple modularity \cite{nicosia2009extending}
    \[
Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
\]

@@

\begin{frame}{Network sensitivity analysis}
\label{slide:sensitivity}
\hyperlink{slide:relevance}{\beamerbutton{Back}}

	\includegraphics[width=\textwidth]{figures/commnum_thetaw_byyears.png}
\end{frame}

\begin{frame}{Network sensitivity analysis ($T_W = 2$)}
	\includegraphics[width=\textwidth]{figures/commnum_thetaw_byyears_window3.png}
\end{frame}

\begin{frame}{Network sensitivity analysis}
	\includegraphics[width=\textwidth]{figures/vcount_comnum_pareto.png}
\end{frame}

\begin{frame}{Network sensitivity analysis ($T_W = 2$)}
	\includegraphics[width=\textwidth]{figures/vcount_comnum_pareto_window3.png}
\end{frame}

\begin{frame}{Network sensitivity analysis}
	\includegraphics[width=\textwidth]{figures/normalizedObjs-dispth_eth4_1e-5.png}
\end{frame}

\begin{frame}{Network sensitivity analysis ($T_W = 2$)}
	\includegraphics[width=\textwidth]{figures/normalizedObjs-dispth_window3_eth4_1e-5.png}
\end{frame}
